---
title: "Introduction to SCMs: Synthetic Control Methods with Specification Curve Analysis"
author: "SCMs Package Authors"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    fig_width: 8
    fig_height: 6
vignette: >
  %\VignetteIndexEntry{Introduction to SCMs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/intro-",
  warning = FALSE,
  message = FALSE
)
```

# Introduction

The **SCMs** package provides a comprehensive implementation of synthetic control methods with advanced specification curve analysis and machine learning integration. This vignette introduces the key concepts and basic usage patterns.

## What are Synthetic Control Methods?

Synthetic control methods allow researchers to estimate the causal effect of an intervention on a treated unit by constructing a "synthetic" version of the treated unit using a weighted combination of control units. The method is particularly useful for:

- Policy evaluation with a single treated unit (e.g., a state, country, or firm)
- Settings where randomized experiments are not feasible
- Time series data with pre- and post-treatment periods

## Why Specification Curve Analysis?

Traditional synthetic control studies typically present results from a single specification. However, researchers must make many modeling choices:

- Which pre-treatment characteristics to match on?
- How to aggregate covariates over time?
- Which optimization constraints to use?
- What feature weighting scheme to employ?

**Specification curve analysis** systematically varies these choices and examines the distribution of treatment effect estimates across all reasonable specifications. This approach:

1. **Increases transparency** by showing the full range of plausible estimates
2. **Assesses robustness** by revealing whether conclusions depend on specific choices
3. **Identifies drivers** of variation in results through SHAP value analysis

## Package Highlights

The SCMs package offers several innovations:

- **Comprehensive specification spaces**: Systematically vary modeling choices
- **SHAP integration**: Use machine learning to understand what drives variation in results
- **Advanced inference**: Both Abadie placebo tests and bootstrap methods
- **Performance optimization**: Handle large specification curves efficiently
- **Professional visualization**: Publication-ready plots with ggplot2

## Basic Workflow

A typical analysis follows this pattern:

1. **Prepare data**: Panel data in long format
2. **Run specification curve**: Systematically vary modeling choices
3. **Visualize results**: Examine the distribution of treatment effects
4. **Interpret patterns**: Use SHAP values to understand variation
5. **Draw conclusions**: Assess robustness and policy implications

# Quick Start Example

Let's demonstrate the package with a simple example using simulated data.

```{r load-packages}
library(SCMs)
library(data.table)
library(ggplot2)

# For reproducibility
set.seed(123)
```

## Create Example Data

```{r create-data}
# Create panel data for demonstration
states <- c("California", "Texas", "New York", "Florida", "Illinois")
years <- 1990:2010

# Generate full panel
panel_data <- expand.grid(
  state = states,
  year = years,
  stringsAsFactors = FALSE
)

# Convert to data.table for efficiency
setDT(panel_data)

# Add outcome variable with treatment effect for California after 2000
panel_data[, gdp := 100 + (year - 1990) * 1.5 + rnorm(.N, 0, 3)]
panel_data[state == "California" & year > 2000, gdp := gdp + 8]

# Add covariates
panel_data[, population := 1000 + (year - 1990) * 50 + rnorm(.N, 0, 100)]
panel_data[, investment := 20 + gdp * 0.15 + rnorm(.N, 0, 5)]

# Display sample of data
head(panel_data, 10)
```

## Basic Synthetic Control Analysis

Let's start with a single specification to understand the core methodology:

```{r basic-scdata, eval=FALSE}
# Prepare synthetic control data
scdata_result <- scdata(
  df = panel_data,
  id.var = "state",
  time.var = "year", 
  outcome.var = "gdp",
  period.pre = 1990:2000,
  period.post = 2001:2010,
  unit.tr = "California",
  unit.co = c("Texas", "New York", "Florida", "Illinois"),
  covagg = list(
    list(var = "population"),
    list(var = "investment")
  )
)

# Estimate synthetic control weights
scest_result <- scest(
  data = scdata_result,
  w.constr = list(name = "simplex"),
  feature_weights = "uniform"
)

# View results
print(scest_result)
summary(scest_result)
```

## Specification Curve Analysis

Now let's examine robustness by varying multiple modeling choices:

```{r spec-curve, eval=FALSE}
# Define covariate specifications to test
covariate_specs <- list(
  # Basic specification
  basic = list(
    label = "basic",
    operations = list(
      list(var = "population", compute = "mean"),
      list(var = "investment", compute = "mean")
    )
  ),
  
  # Include outcome lags
  with_lags = list(
    label = "with_lags", 
    operations = list(
      list(var = "outcome_var", partition_periods = list(type = "by_period")),
      list(var = "population", compute = "mean"),
      list(var = "investment", compute = "mean")
    )
  ),
  
  # Population only
  population_only = list(
    label = "population_only",
    operations = list(
      list(var = "population", compute = "mean")
    )
  )
)

# Run specification curve analysis
spec_results <- run_spec_curve_analysis(
  dataset = panel_data,
  outcomes = "gdp",
  covagg_list = covariate_specs,
  col_name_unit_name = "state",
  name_treated_unit = "California", 
  treated_period = 2001,
  min_period = 1990,
  end_period = 2010,
  col_name_period = "year",
  
  # Modeling choices to vary
  feature_weights = c("uniform", "optimize"),
  outcome_models = c("none", "ridge"),
  constraints = list(
    list(name = "simplex"),
    list(name = "lasso", Q = 0.1)
  ),
  
  # Inference settings
  inference_type = "placebo",
  cores = 1,  # Use 1 core for vignette
  verbose = TRUE
)

# View specification curve
plot(spec_results)
```

# Understanding the Output

## Treatment Effect Distribution

The specification curve shows:

- **X-axis**: Individual specifications (sorted by effect size)
- **Y-axis**: Treatment effect estimates
- **Points**: Each specification's estimate
- **Colors**: SHAP values indicating which features drive the estimates

## Key Interpretations

1. **Central tendency**: Where do most estimates cluster?
2. **Range**: How wide is the distribution of plausible effects?
3. **Outliers**: Are there specifications with very different results?
4. **Patterns**: Do certain modeling choices systematically affect results?

## Statistical Inference

The package provides two inference approaches:

1. **Abadie Placebo Tests**: Compare treated unit's post/pre RMSPE ratio to control units
2. **Bootstrap Methods**: Construct null distributions for hypothesis testing

## SHAP Value Interpretation

SHAP (SHapley Additive exPlanations) values help understand:

- Which pre-treatment features are most predictive
- How feature importance varies across specifications
- Whether results are driven by specific covariates

# Next Steps

This introduction covered the basic concepts and workflow. To learn more:

- **Complete Workflow** vignette: Step-by-step analysis with real data
- **Advanced Features** vignette: Customization, optimization, and extensions
- **Package documentation**: `help(package = "SCMs")`

The synthetic control method with specification curve analysis provides a powerful framework for causal inference with observational data. The SCMs package makes these advanced methods accessible while maintaining statistical rigor and computational efficiency.

# References

- Abadie, A., Diamond, A., & Hainmueller, J. (2010). Synthetic control methods for comparative case studies. *Journal of the American Statistical Association*, 105(490), 493-505.

- Simonsohn, U., Simmons, J. P., & Nelson, L. D. (2020). Specification curve analysis. *Nature Human Behaviour*, 4(11), 1208-1214.

- Ben-Michael, E., Feller, A., & Rothstein, J. (2021). The augmented synthetic control method. *Journal of the American Statistical Association*, 116(536), 1789-1803.
